---
title: "R Notebook"
output: html_notebook
---

```{r}

# Perform PCA on mtcars (using only numeric columns)
mtcars_pca <- prcomp(mtcars, scale. = TRUE)

# Convert PCA scores to a data frame
mtcars_pca_df <- as.data.frame(mtcars_pca$x)

# Add a car name column for reference
mtcars_pca_df$car <- rownames(mtcars)

# Plot the first two principal components
library(ggplot2)

mtcars_after_pca <- ggplot(mtcars_pca_df, aes(x = PC1, y = PC2)) +
  geom_point(color = "blue", size = 3) +
  geom_text(aes(label = car), vjust = 1.5, size = 3) +
  xlab("PCA 1") +
  ylab("PCA 2") +
  theme_minimal()

print(mtcars_after_pca)
plot(cars)
```
```{r}

```









Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
